Automatic Matching of Bullet Lands

### 2016-01-06 imaging-paper.Rnw
to do list out

\hh{
Todo list for journal shape-up: there is a lot of good material, we mainly need to focus on what story to tell and make that a solid argument.
\begin{enumerate}

@@

\item add: should we add a paragraph on the speed of the evaluation? - separate out into pre-processing (needs to be done once) and matching (pairwise comparison of lands). If we only do bullet matching, we could speed this process up by eliminating some land comparisons. - Thinking about this more, I'm against it. The speed massively depends on the kind of computer used - the important thing is, that on a server all of these calculations are very fast -- even my machine can do 11 comparisons per second, if the files are pre-processed. Pre-processing might take a couple of seconds - at most 20-30 seconds for each bullet land. That is an initial cost one has to pay.

@@

\item to consider: AOAS states that accepted papers rarely have more than 20 pages. We are currently over by a couple of pages.

@@

\end{enumerate}
}

@@

>>>>

%\hh{
%Todo list for journal shape-up: there is a lot of good material, we mainly need to focus on what story to tell and make that a solid argument.
%\begin{enumerate}

@@

%\item add: should we add a paragraph on the speed of the evaluation? - separate out into pre-processing (needs to be done once) and matching (pairwise comparison of lands). If we only do bullet matching, we could speed this process up by eliminating some land comparisons. - Thinking about this more, I'm against it. The speed massively depends on the kind of computer used - the important thing is, that on a server all of these calculations are very fast -- even my machine can do 11 comparisons per second, if the files are pre-processed. Pre-processing might take a couple of seconds - at most 20-30 seconds for each bullet land. That is an initial cost one has to pay.

@@

%\item to consider: AOAS states that accepted papers rarely have more than 20 pages. We are currently over by a couple of pages.

@@

%\end{enumerate}
%}

@@

\hh{XXX speed? XXX}
